|

### 2024-05-09 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Methods results done

 # if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000

@@

  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
  # So the R in 1970 were produced by SSB in 1969 when min age =0
  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
  # that gets us to the babies that show up in 1970
  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  tmp <- NULL
  for(j in 1:length(years))
  {
    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
    tmp[[j]] <- tst
  }
  # Unpack the list
  ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

@@

  for.tune.all.res <- NULL
  for.tune.summary <- NULL
  for(i in Stocks)
  {
    years <- years.tmp[[i]]
    prop.nat.mort <- pnm.tmp[[i]] 
    #rem <- rem.tmp[[i]] 
    mx <- mx.tmp[[i]] 
    N.end <- NE.tmp[[i]] 
    ages <- ages.tmp[[i]]
    vpa.abund <- vpa.tmp[[i]] 
    abund <- abund.tmp[[i]]
    fs <-fs.tmp[[i]]
    full.rem <- rem.tmp[[i]]
    #full.abund <- full.abund.tmp[[i]]
    #all.abund <- full.abund.tmp[[i]]
    #N.end <- vpa.abund[length(vpa.abund)]
    #Pick your step size
    ss.size <- 0.005
    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
                            "DFO_2J3KL_Gadus_morhua",
                            "DFO_3Pn-4RS_Gadus_morhua",
                            "DFO_4T-4VN_Gadus_morhua",
                            "DFO_4T_Scomber_scombrus",
                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
                            "ICES-AFWG_NEA1-2_Gadus_morhua",
                            "ICES-HAWG_NS_Ammodytes_dubius",
                            "ICES-NWWG_FA5b_Pollachius_virens",
                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
                            "ICES-WGCSE_IS7a_Gadus_morhua",
                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
                            "NEFSC_NWA_Scomber _scombrus")

  #NE Arctic aeglefinus (high and lows)  (21) solved
  #Faroes 5b P. virens (high and lows)  (29) solved

@@

  # First making a meta data object and adding a bunch of columns to it... very messy!!
  meta$Species[meta$Species == ' harengus']  <- "harengus"
  meta$Species[meta$Species == "Aeglefinus"] <- "aeglefinus"
  meta$Species[meta$Species == "Solea"] <- "solea"
  meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
  meta$G.short <- toupper(paste0(substr(meta$Genus,1,1),"."))
  meta$G.Species <- paste0(meta$G.short," ",meta$Species)
  # Simplified Management
  meta$Manage.short <- meta$Management
  meta$Manage.short[grep("TRAC",meta$Management)] <- "DFO-TRAC"
  meta$Manage.short[grep("DFO",meta$Management)] <- "DFO-TRAC"
  meta$Manage.short[grep("NEFSC",meta$Management)] <- "NEFSC"
  meta$Manage.short[grep("ICES",meta$Management)] <- "ICES"

  # The 3 pieces of the ocean
  meta$LME <- "NW Atlantic"
  meta$LME[meta$Management == "AFSC"] <- "Pacific (Alaska)"
  meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
  # Some other Area summaries
  meta$Area.broad <- meta$Area
  meta$Area.long <- meta$Area
  meta$Area.narrow <- "" # Leave this blank if not needed

  meta$Area.broad[grep("NS",meta$Area)] <- "NS"
  meta$Area.long[grep("NS",meta$Area)] <- "North Sea"
  meta$Area.broad[grep("CS",meta$Area)] <- "CS"
  meta$Area.long[grep("CS",meta$Area)] <- "Celtic Sea"
  meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
  meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea Rockall"
  meta$Area.broad[grep("IS",meta$Area)] <- "IS"
  meta$Area.long[grep("IS",meta$Area)] <- "Irish Sea"
  meta$Area.broad[grep("BS",meta$Area)] <- "BS"
  meta$Area.long[grep("BS",meta$Area)] <- "Baltic Sea"
  meta$Area.broad[grep("NEA",meta$Area)] <- "NEA"
  meta$Area.long[grep("NEA",meta$Area)] <- "NE Arctic"
  meta$Area.broad[grep("B28.1",meta$Area)] <- "BS"
  meta$Area.long[grep("B28.1",meta$Area)] <- "Baltic Sea"
  meta$Area.broad[grep("SP8abd",meta$Area)] <- "BoB"
  meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
  meta$Area.broad[grep("FA",meta$Area)] <- "I-F"
  meta$Area.broad[grep("ICE",meta$Area)] <- "I-F"
  meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
  meta$Area.long[grep("ICE",meta$Area)] <- "Iceland"

  meta$Area.broad[grep("GOM",meta$Area)] <- "GOM-GB"
  meta$Area.long[grep("GOM",meta$Area)] <- "Gulf of Maine"
  meta$Area.broad[grep("GB",meta$Area)] <- "GOM-GB"
  meta$Area.long[grep("GB",meta$Area)] <- "Georges Bank"
  meta$Area.broad[grep("5Y",meta$Area)] <- "GOM-GB"
  meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5Y"
  meta$Area.broad[grep("5Z",meta$Area)] <- "GOM-GB"
  meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5Z"
  meta$Area.broad[grep("USATL",meta$Area)] <- "GOM-GB" # The fishery is broader than just GOM, but it does also include it.
  meta$Area.long[grep("USATL",meta$Area)] <- "US Atlantic" # The fishery is broader than just GOM, but it does also include it.
  meta$Area.broad[grep("NWA",meta$Area)] <- "GOM-GB" # Mackerel... so that definition is a bit narrow....
  meta$Area.long[grep("NWA",meta$Area)] <- "US Atlantic" # Mackerel... so that definition is a bit narrow....

@@

  meta$Area.broad[grep("MA",meta$Area)] <- "GOM-GB" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
  meta$Area.long[grep("MA",meta$Area)] <- "Gulf of Maine" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....

@@

  meta$Area.broad[grep("4T",meta$Area)] <- "GSL"
  meta$Area.long[grep("4T",meta$Area)] <- "NAFO 4T"
  meta$Area.broad[grep("2J3",meta$Area)] <- "NFLD"
  meta$Area.long[grep("2J3",meta$Area)] <- "NFLD"
  meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NFLD"
  meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NFLD"

@@

@@

  meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea"

@@

  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"

@@

  meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fall"
  meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Spring"

@@

  meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "2J 3KL"
  meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "3Pn 4RS"
  meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "East"

  meta$Stock.short <- paste0(meta$Area.long," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
  meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)

@@

  # Doubling time, no fishing
  dt.res <- NULL
  n.dt.sims <- 1000 # Increase to 1000 for final run, which takes like a full day or something 
  n.years <- 100
  for(i in Stocks)
  {
    str.time <- Sys.time()
    try <- for.tune.all[[i]]
    meta.tmp <- try$meta
    age.4.sim <- meta.tmp$age.min:meta.tmp$age.max
    double.time <- NA
    pop <- 1000
    tmp.res <- NULL
  for(s in 1:n.dt.sims)
  {

    tmp <- rep(0,n.years)
    for(y in 2:n.years)
    {

      # Get our sample for this run
      f.pick <- sample(nrow(try$fecund.opt),size=1)
      nm.pick <- sample(nrow(try$nm.opt),size=1)
      fec.samp <- try$fecund.opt[f.pick,]
      # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
      nm.samp <- try$nm.opt[nm.pick,] 
      # now put these into Euler-lotka to get an r estimate
      res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
      r.val <- res$res$r
      # If r is > 5 (lambda = exp(5)) it generally means the simple.lotka didn't converge (bad combo of fec and nm)
      # So we'll need to resample them until it is < 5
      while(r.val >= 5)
      {
        print("Resampling due to bat shit r value")
        f.pick <- sample(nrow(try$fecund.opt),size=1)
        nm.pick <- sample(nrow(try$nm.opt),size=1)
        fec.samp <- try$fecund.opt[f.pick,]
        # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
        nm.samp <- try$nm.opt[nm.pick,] 
        # now put these into Euler-lotka to get an r estimate
        res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
        r.val <- res$res$r
      } # end while loop
      pop[y] <- exp(r.val)*pop[y-1]
      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.years] <- 1
    } # end the years loop
    tmp.res[[s]] <- data.frame(year =1:n.years,doubled = tmp,sim=s)

@@

  dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
  count <- 0
  print(paste0("Stock ",i," Sim ", s," time =", round(Sys.time()-str.time,digits=1)," minutes Stock number",count+1))
  } # end Stocks loop

@@

      for(a in 1:n.ages)
      {
      fs[a] <- fec.tmp[y+count,a]  
      fs.org[a] <- fec.org.tmp[y+count,a]  
      if(a > 1) 
      {
        # No fishing
        lx[a] <- lx[a-1] * m.tmp[y+count,a]  
        lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
        lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
        # Including fishing
        zx[a] <- zx[a-1] * z.tmp[y+count,a]  
        zx.org[a] <- zx.org[a-1]* z.org.tmp[y+count,a]  
        zx.year[a] <- zx.year[a-1] * z.tmp[y,a]
      }  # end the a > 1 if
          count <- count + 1
      }# end the ages loop
          res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.opt = lx,
                                 mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                                 x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
                                 zx.opt = zx,zx.opt = zx,
                                 mx.zx.opt = fs*zx,mx.zx.org = fs.org*zx.org,
                                 x.mx.zx.opt = fs*zx*ages,x.mx.zx.org = fs.org*zx.org*ages,
                                 cohort=years[y],age = ages,meta.tmp)

@@

  pop.dam <- res.cohort.final |> dplyr::group_by(cohort,Stock) |> dplyr::summarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
                                                                  gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
                                                                  R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
  pop.dam <- left_join(pop.dam,meta.sub,by="Stock")

@@

```{r simp-figs,include=F,echo=F,message=F,warning=F}
load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
res.lambda.fin <- data.frame(res.lambda.final)

six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
pop.dam.6 <- pop.dam |> collapse::fsubset(Species %in% six.species)
for.tunes.6 <- for.tunes |> collapse::fsubset(Species %in% six.species)
dub.time.6 <- dub.time.summary |> collapse::fsubset(Species %in% six.species)
res.lambda.fin$decade <- floor(res.lambda.fin$year/10)*10
res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock,decade) |> collapse::fmutate(mn.lam = mean(lam.fish,na.rm=T),
                                                                                 med.lam = median(lam.fish,na.rm=T),
                                                                                 sd.lam = sd(lam.fish,na.rm=T))
res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Species,decade) |> collapse::fmutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
res.lambda.fin <- res.lambda.fin |> collapse::fgroup_by(Stock) |> 
                                                          collapse::fmutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
                                                          lam.fish.med = median(lam.fish,na.rm=T),
                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T)) |> data.frame()

res.lambda.final.6 <- res.lambda.fin |> collapse::fsubset(Species %in% six.species)
# Sort the data into a nice order...
res.lambda.fin <- res.lambda.fin |> collapse::roworder(Species,Area.broad) |>
                                    collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
res.lambda.final.6 <- res.lambda.final.6 |> collapse::roworder(Species,Area.broad) |>
                                            collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
dub.time <- dub.time |> collapse::roworder(LME) |>
                        collapse::fmutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))

>>>>

@@

  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
  # So the R in 1970 were produced by SSB in 1969 when min age =0
  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
  # that gets us to the babies that show up in 1970
  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  tmp <- NULL
  for(j in 1:length(years))
  {
    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
    tmp[[j]] <- tst
  }
  # Unpack the list
  ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])

@@

  for.tune.all.res <- NULL
  for.tune.summary <- NULL
  for(i in Stocks)
  {
    years <- years.tmp[[i]]
    prop.nat.mort <- pnm.tmp[[i]] 
    #rem <- rem.tmp[[i]] 
    mx <- mx.tmp[[i]] 
    N.end <- NE.tmp[[i]] 
    ages <- ages.tmp[[i]]
    vpa.abund <- vpa.tmp[[i]] 
    abund <- abund.tmp[[i]]
    fs <-fs.tmp[[i]]
    full.rem <- full.rem.tmp[[i]]
    #full.abund <- full.abund.tmp[[i]]
    #all.abund <- full.abund.tmp[[i]]
    #N.end <- vpa.abund[length(vpa.abund)]
    #Pick your step size
    ss.size <- 0.005
    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
                            "DFO_2J3KL_Gadus_morhua",
                            "DFO_3Pn-4RS_Gadus_morhua",
                            "DFO_4T-4VN_Gadus_morhua",
                            "DFO_4T_Scomber_scombrus",
                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
                            "ICES-AFWG_NEA1-2_Gadus_morhua",
                            "ICES-HAWG_NS_Ammodytes_dubius",
                            "ICES-NWWG_FA5b_Pollachius_virens",
                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
                            "ICES-WGCSE_IS7a_Gadus_morhua",
                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
                            "NEFSC_NWA_Scomber _scombrus")

@@

  # First making a meta data object and adding a bunch of columns to it... very messy!!
  meta$Species[meta$Species == ' harengus']  <- "harengus"
  meta$Species[meta$Species == "Aeglefinus"] <- "aeglefinus"
  meta$Species[meta$Species == "Solea"] <- "solea"
  meta$Family[meta$Family == "Gadide"] <- "Gadidae"
  meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
  meta$G.short <- toupper(paste0(substr(meta$Genus,1,1),"."))
  meta$G.Species <- paste0(meta$G.short," ",meta$Species)
  # Simplified Management
  meta$Manage.short <- meta$Management
  meta$Manage.short[grep("TRAC",meta$Management)] <- "DFO-TRAC"
  meta$Manage.short[grep("DFO",meta$Management)] <- "DFO-TRAC"
  meta$Manage.short[grep("NEFSC",meta$Management)] <- "NEFSC"
  meta$Manage.short[grep("ICES",meta$Management)] <- "ICES"

  # The 3 pieces of the ocean
  meta$LME <- "NW Atlantic"
  meta$LME[meta$Management == "AFSC"] <- "Pacific (Alaska)"
  meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
  # An area typo
  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI-Females"
  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
  # Some other Area summaries
  meta$Area.broad <- meta$Area
  meta$Area.long <- meta$Area
  meta$Area.narrow <- "" # Leave this blank if not needed

  meta$Area.broad[grep("NS",meta$Area)] <- "NS"
  meta$Area.long[grep("NS",meta$Area)] <- "North Sea"
  meta$Area.broad[grep("CS",meta$Area)] <- "CS"
  meta$Area.long[grep("CS",meta$Area)] <- "Celtic Sea"
  meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
  meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea"
  meta$Area.broad[grep("IS",meta$Area)] <- "IS"
  meta$Area.long[grep("IS",meta$Area)] <- "Irish Sea"
  meta$Area.broad[grep("BS",meta$Area)] <- "BS"
  meta$Area.long[grep("BS",meta$Area)] <- "Baltic Sea"
  meta$Area.broad[grep("NEA",meta$Area)] <- "NEA"
  meta$Area.long[grep("NEA",meta$Area)] <- "NE Arctic"
  meta$Area.broad[grep("B28.1",meta$Area)] <- "BS"
  meta$Area.long[grep("B28.1",meta$Area)] <- "Baltic Sea"
  meta$Area.broad[grep("SP8abd",meta$Area)] <- "BoB"
  meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
  meta$Area.broad[grep("FA",meta$Area)] <- "Ice-Faroe"
  meta$Area.broad[grep("ICE",meta$Area)] <- "Ice-Faroe"
  meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
  meta$Area.long[grep("ICE",meta$Area)] <- "Iceland"

  meta$Area.broad[grep("GOM",meta$Area)] <- "NAFO 5-6"
  meta$Area.long[grep("GOM",meta$Area)] <- "NAFO 5-6"
  meta$Area.broad[grep("GB",meta$Area)] <- "NAFO 5-6"
  meta$Area.long[grep("GB",meta$Area)] <- "NAFO 5-6"
  meta$Area.broad[grep("5Y",meta$Area)] <- "NAFO 5-6"
  meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5-6"
  meta$Area.broad[grep("5Z",meta$Area)] <- "NAFO 5-6"
  meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5-6"
  meta$Area.broad[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
  meta$Area.long[grep("USATL",meta$Area)] <- "NAFO 5-6" # The fishery is broader than just GOM, but it does also include it.
  meta$Area.broad[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....
  meta$Area.long[grep("NWA",meta$Area)] <- "NAFO 5-6" # Mackerel... so that definition is a bit narrow....

@@

  meta$Area.broad[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
  meta$Area.long[grep("MA",meta$Area)] <- "NAFO 5-6" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....

@@

  meta$Area.broad[grep("4T",meta$Area)] <- "NAFO 2-4"
  meta$Area.long[grep("4T",meta$Area)] <- "NAFO 2-4"
  meta$Area.broad[grep("2J3",meta$Area)] <- "NAFO 2-4"
  meta$Area.long[grep("2J3",meta$Area)] <- "NAFO 2-4"
  meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"
  meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NAFO 2-4"

@@

  # Lumping everything in Berring Sea and AI into both.

@@

  meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea & AI" 

@@

  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI"
  meta$Area[grep("BSAI-Females",meta$Area)] <- "BSAI"
  meta$Area[grep("BSAI-females",meta$Area)] <- "BSAI"

@@

  meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fa-SGSL"
  meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Sp-SGSL"

@@

  meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "NFLD"
  meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "NGSL"
  meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "EGB"
  meta$Area.narrow[meta$Stock == "ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus"] <- "RA"
  meta$Area.narrow[meta$Stock == "DFO_4T-4VN_Gadus_morhua"] <- "SGSL"
  meta$Area.narrow[meta$Stock == "DFO_4T_Hippoglossoides _platessoides"] <- "SGSL"
  meta$Area.narrow[meta$Stock == "DFO_4T_Scomber_scombrus"] <- "SGSL"
  meta$Area.narrow[meta$Stock == "NEFSC-SAW_GOM_Gadus_morhua"] <- "GOM"
  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_GB_Gadus_morhua"] <- "GB"
  meta$Area.narrow[meta$Stock == "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus"] <- "GOM"
  meta$Area.narrow[meta$Stock == "CERT-TRAC_GB_Melanogrammus_Aeglefinus"] <- "GB"

  meta$Stock.short <- paste0(meta$Area.broad," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
  meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)

@@

  # Doubling time, no fishing
  dt.res <- NULL
  # These are both set in the index file now, go there!!
  n.dt.sims <- n.dt.sims
  n.sim.years <- n.sim.years
  for(i in Stocks)
  {
    str.time <- Sys.time()
    try <- for.tune.all[[i]]
    meta.tmp <- try$meta
    age.4.sim <- meta.tmp$age.min:meta.tmp$age.max
    double.time <- NA
    pop <- 1000
    tmp.res <- NULL
  for(s in 1:n.dt.sims)
  {
    tmp <- rep(0,n.sim.yearss)
    print(paste0("Sim # ", s))

    for(y in 2:n.sim.yearss)
    {

      # Get our sample for this run
      f.pick <- sample(nrow(try$fecund.opt),size=1)
      nm.pick <- sample(nrow(try$nm.opt),size=1)
      fec.samp <- try$fecund.opt[f.pick,]
      # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
      nm.samp <- try$nm.opt[nm.pick,] 
      # now put these into Euler-lotka to get an r estimate
      res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
      r.val <- res$res$r
      # If r is > 5 (lambda = exp(5)) it generally means the simple.lotka didn't converge (bad combo of fec and nm)
      # So we'll need to resample them until it is < 5
      while(r.val >= 5)
      {
        print("Resampling due to bat shit r value")
        f.pick <- sample(nrow(try$fecund.opt),size=1)
        nm.pick <- sample(nrow(try$nm.opt),size=1)
        fec.samp <- try$fecund.opt[f.pick,]
        # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
        nm.samp <- try$nm.opt[nm.pick,] 
        # now put these into Euler-lotka to get an r estimate
        res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
        r.val <- res$res$r
      } # end while loop
      pop[y] <- exp(r.val)*pop[y-1]
      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.sim.yearss] <- 1
    } # end the years loop
    tmp.res[[s]] <- data.frame(year =1:n.sim.yearss,doubled = tmp,sim=s)

@@

  dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
  count <- 0
  timer <- round(difftime(Sys.time(),str.time,units='mins'),digits=1)
  print(paste0("Stock ",i," time =", timer," minutes: Stock # ",count+1))
  } # end Stocks loop

@@

      for(a in 1:n.ages)
      {
      fs[a] <- fec.tmp[y+count,a]  
      fs.org[a] <- fec.org.tmp[y+count,a]  
      if(a > 1) 
      {
        # No fishing
        lx[a] <- lx[a-1] * m.tmp[y+count,a]  
        lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
        lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
        # Including fishing
        zx[a] <- zx[a-1] * z.tmp[y+count,a]  
        zx.org[a] <- zx.org[a-1]* z.org.tmp[y+count,a]  
        zx.year[a] <- zx.year[a-1] * z.tmp[y,a]
      }  # end the a > 1 if
          count <- count + 1
      }# end the ages loop
          res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,
                                 mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                                 x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
                                 zx.opt = zx,
                                 mx.zx.opt = fs*zx,mx.zx.org = fs.org*zx.org,
                                 x.mx.zx.opt = fs*zx*ages,x.mx.zx.org = fs.org*zx.org*ages,
                                 cohort=years[y],age = ages,meta.tmp)

@@

  pop.dam <- res.cohort.final |> collapse::fgroup_by(cohort,Stock) |> collapse::fsummarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
                                                                                   gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
                                                                                   R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
  pop.dam <- left_join(pop.dam,meta.sub,by="Stock")

@@

```{r clean-up-and-stats,include=F,echo=F,message=F,warning=F}
load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
